---
title: "OAmonitor R package"
author:
  - Kristina Hettne^[Leiden University Libraries, https://orcid.org/0000-0002-4182-7560]
  - Barbara Vreede^[Utrecht University, https://orcid.org/0000-0002-5023-4601]

date: "Last updated on `r format(Sys.time(), '%d %B, %Y')`"

output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{OAmonitor}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction
This vignette explains the use of the OAmonitor package. We first go through the functionalities of the package and then provide an example for use.

## Package overview
The OAmonitor takes publication data from a single year and determines per article its open access status, using the Directory of Open Access Journals, (DOAJ), Unpaywall and the association of universities in the Netherlands (VSNU) Open Access publishing deals (an excel sheet available through the VSNU). It uses peer reviewed journal articles registered in CRIS systems as input. It was created in a collaboration between Utrecht University Library and Leiden University Library.

## OAmonitor basics
The OAmonitor has three basic parts: data gathering and cleaning, data classification and results reporting. Before user data can be loaded it needs to be in a specific format.

### User data preparation


### Data gathering and cleaning


### Data classification


### Results reporting

## Example

### Setup
```{r setup}
remotes::install_github("https://github.com/bvreede/OAmonitor")
library(OAmonitor)
library(tidyverse)
```

### Input data

Load all files in the excel template
```{r}


```

