---
title: "OAmonitor R package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{OAmonitor}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
Kristina Hettne and Barbara Vreede
Date

## Introduction
This vignette explains the use of the OAmonitor package.

## Package overview
The OAmonitor takes publication data from a single year and determines per article its open access status, using the Directory of Open Access Journals, (DOAJ), Unpaywall and the association of universities in the Netherlands (VSNU) Open Access publishing deals (an excel sheet available through the VSNU). It uses peer reviewed journal articles registered in CRIS systems as input. It was created in a collaboration between Utrecht University Library and Leiden University Library.

## OAmonitor basics
### Mock data
```{r setup}
library(OAmonitor)

```

### Own data
Fill out the excel template like so:

Then load all files in the excel template
```{r}


```

